An Adolescent Mini-Neptune in the Kepler Field

### 2021-07-30 paper/ms.tex
update extinction correction to Gaia2018

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected members of the $\delta$\,Lyr
    cluster.  Both Kepler (gray squares) and TESS (colored points)
    observed portions of the cluster.  Naked-eye stars ($m_{\rm
    V}<6.5$) are shown in gray; four of them (orange points) have
    their names annotated.  Kepler\,1627 (green star) was observed
    during the entirety of the Kepler mission, and has been observed
    by TESS for two lunar months to date.
		\label{fig:skychart}
	}
\end{figure}

@@

\subsection{HR Diagram}
We meaured the isochrone age using an empirical approach, and also
compared against theoretical models.
The left panel of Figure~\ref{fig:age} shows the HR diagram of 
stars in the \cn, the Pleiades, IC\,2602, and the field.
The stars shown in the \cn\ are selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.
% FIXME FIXME
We corrected for reddening following {\bf procedure X,Y,Z}.

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected members of the $\delta$\,Lyr
    cluster.  Both Kepler (gray squares) and TESS 
    observed portions of the cluster.  Naked-eye stars ($m_{\rm
    V}<6.5$) are shown in gray; four of them (orange points) have
    their names annotated.  Kepler\,1627 (green star) was observed
    during the entirety of the Kepler mission, and has been observed
    by TESS for two lunar months to date.
    The colors of the other cluster members indicate the number of
    TESS sectors during which they have been observed.
		\label{fig:skychart}
	}
\end{figure}

@@

\subsection{HR Diagram}
We meaured the isochrone age using an empirical approach, and also
compared against theoretical models.  The left panel of
Figure~\ref{fig:age} shows the HR diagram of stars in the \cn, the
Pleiades, IC\,2602, and the field.  The stars shown in the \cn\ are
selected based on their positions and kinematics, as discussed in
Appendix~\ref{app:kinematicselection}.  Those from the Pleiades and
IC\,2602 are adopted from \citet{cantatgaudin_gaia_2018}, and the
field stars are from the Gaia EDR3 Catalog of Nearby Stars
\citep{gaia_gcns_2021}.  We cleaned these following identical data
filtering criteria to those discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we loosened the parallax
precision requirement to $\texttt{parallax\_over\_error}>5$.  These
filters were designed to include genuine binaries while omitting
instrumental artifacts.  We then corrected for extinction by querying
the 3-D maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and by then using the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018}, while assuming that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleaides, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019},
and have the benefit of being sensitive to effects such as
differential reddening that may be present in the dust maps.

% Gaia+2018 E(B-V):
% Pleiades 0.045, IC2602 0.031
%
% Randich+2018 E(B-V):
% Pleiades ??, IC2602 0.032 - 0.092
%
% KC2019: AV->E(B-V)
% Pleiades 0.220 AV -> 0.071
% IC2602 0.243297 -> 0.078
% Stephenson1 0.184 -> 0.059
%
% Bossini+2019 AV->E(B-V)
% PleiadesMelotte22 0.140 -> 0.045
% IC2602 0.096 -> 0.031
% Steph1: 0.157 -> 0.051

following {\bf procedure X,Y,Z}.
